SDR enhancement by clouds \\\large{A Short Subtitle}

### 2023-11-28 article/article.tex
Commit 2023-11-28 08:14

\begin{keyword}
    keyword1 \sep 
    keyword2
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, breakable, interior hidden, enhanced, boxrule=0pt, sharp corners, frame hidden]}{\end{tcolorbox}}\fi

@@

Clear sky identification

Criteria for enhancement based on TSI

@@

@@

\begin{tcolorbox}[enhanced jigsaw, left=2mm, title=\textcolor{quarto-callout-important-color}{\faExclamation}\hspace{0.5em}{gcff}, toptitle=1mm, leftrule=.75mm, colframe=quarto-callout-important-color-frame, rightrule=.15mm, opacitybacktitle=0.6, bottomtitle=1mm, titlerule=0mm, arc=.35mm, breakable, opacityback=0, bottomrule=.15mm, toprule=.15mm, colbacktitle=quarto-callout-important-color!10!white, coltitle=black, colback=white]

>>>>

\begin{keyword}
    keyword1 \sep 
    keyword2
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, breakable, boxrule=0pt, frame hidden, interior hidden, enhanced, sharp corners]}{\end{tcolorbox}}\fi

@@

Clear sky identification - helps on determining thresholds

Criteria for enhancement based on TSI - some other were tested

@@

\begin{itemize}
\tightlist
\item
  max
\item
  seasonal
\item
  trends
\item
  duration
\item
  occurrence
\item
  SZA
\end{itemize}

@@

\begin{tcolorbox}[enhanced jigsaw, colback=white, coltitle=black, left=2mm, colframe=quarto-callout-important-color-frame, rightrule=.15mm, toprule=.15mm, colbacktitle=quarto-callout-important-color!10!white, titlerule=0mm, title=\textcolor{quarto-callout-important-color}{\faExclamation}\hspace{0.5em}{gcff}, leftrule=.75mm, opacityback=0, breakable, bottomtitle=1mm, opacitybacktitle=0.6, toptitle=1mm, arc=.35mm, bottomrule=.15mm]
